---
title: "A3: Incarceration"
output: html_document
---

```{r include=F}
source("summary.R")
```


### Introduction

In this project we will compare the trends of prision admission rate for female and male, we will focus on the following variables:

- year: current year

- state: state name in USA

- county_name: county name

- female_prison_adm_rate: the prision admission rate of female

- female_prison_adm_rate: the prision admission rate of male


### Summary Information

The avearge prison admission rate of female is `r round(stats$female.mean, 2)`, the median prison admission rate of female is `r round(stats$female.median, 2)`, the maximum prison admission rate of female is `r round(stats$female.max, 2)`, the minimum prison admission rate of female is `r round(stats$female.min, 2)`. The avearge prison admission rate of male is `r round(stats$male.mean, 2)`, the median prison admission rate of male is `r round(stats$male.median, 2)`, the maximum prison admission rate of male is `r round(stats$male.max, 2)`, the minimum prison admission rate of male is `r round(stats$male.min, 2)`, so the avearge prison admission rate of male is much higher than the average prison admission rate of female.


### The Dataset
The dataset was collected by Bureau of Justice Statistics (BJS) and Annual Survey of Jails (ASJ), This project was funded by the Robert W. Wilson Charitable Trust.  The county-level variability makes for more robust than the state-level, theoretically-grounded studies of the high rates of incarceration seen across the United States, the dataset contains 153811 observations and 121 variables.

### Trends Over Time Chart

What's the trend of the prison admission rate for female and male? Is there any difference between female and male?

```{r, echo = FALSE, code = readLines("chart1.R"), warning=F, message=F}
```

The figure suggests that both female and male have an increasding trend of the prison admission rate over these years, the average prison admission rate of male is higher than male, there is a sudden decrease in the average prison admission rate for male in around 1983.


### Variable Comparison Chart

What is the relationship between the average prison admission rate of female and the average prison admission rate of male, are they positively linear associated?


```{r, echo = FALSE, code = readLines("chart2.R"), warning=F, message=F}
```

The figure suggests that the average prison admission rate of female is strongly positve linear associated with the average prison admission rate of male, that't to say, when the average prison admission rate of female increases, the average prison admission rate of male also increases.


### Map

```{r, echo = FALSE, code = readLines("map.R"), warning=F, message=F}

```

The map tells us that Warren has the highest prison admission rate of female, Clinton has the second highest prison admisson rate for female, and Hamilton has the lowest prison admission rate for female.
